*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-01 Code/Manuscript_O2.Rmd
Added proper citations

MIT9313 is not “using” photosynthesis in low O~2~ environments to do CO~2~ fixation so much as to generate oxygen locally in an environment that is low enough to limit the ability to do respiration. The deep water environments that we see MIT 9313 are relatively nutrient rich and there is evidence in the literature of *Prochlorococcus* have  been observed to take up and metabolise various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017] and amino acids (Zubkov et al., 2004). They may be using photosynthesis to generate O~2~ to act as an electron sink for respiration. And maybe using ATP to take up food from the surroundings.
Partensky *et al*. [@partenskyComparisonPhotosyntheticPerformances2018] found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels caused the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain could generate and could potentially be contributing to the maintenance of the low O~2~ environment

>>>>

MIT9313 is not “using” photosynthesis in low O~2~ environments to do CO~2~ fixation so much as to generate oxygen locally in an environment that is low enough to limit the ability to do respiration. The deep water environments that we see MIT 9313 are relatively nutrient rich and there is evidence in the literature of *Prochlorococcus* have  been observed to take up and metabolise various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004]. They may be using photosynthesis to generate O~2~ to act as an electron sink for respiration. And maybe using ATP to take up food from the surroundings.
Partensky *et al*. [@partenskyComparisonPhotosyntheticPerformances2018] found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels caused the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain could generate and could potentially be contributing to the maintenance of the low O~2~ environment.
